
\documentclass[letterpaper]{article}

%\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage[semibold]{ebgaramond} % Use the EB Garamond font with a reduced bold weight
\usepackage{titlesec}



% Set your name here
\def\name{Ryan Paul Larson}


% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  linkcolor = teal,
  urlcolor = teal,
  pdfauthor = {\name},
  pdfkeywords = {sociology, statistics, criminology},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}


\geometry{
	paper=letterpaper, % Paper size, change to letterpaper for US letter size
	top=3.25cm, % Top margin
	bottom=4cm, % Bottom margin
	left=3.5cm, % Left margin
	right=3.5cm, % Right margin
	headheight=0.75cm, % Header height
	footskip=1cm, % Space from the bottom margin to the baseline of the footer
	headsep=0.75cm, % Space from the top margin to the baseline of the header
	%showframe, % Uncomment to show how the type block is set on the page
}

%\sectionfont{\fontsize{13.5pt}{18pt}\selectfont} % Set font options for sections
%\subsectionfont{\mdseries\scshape\normalsize} % Set font options for subsections
%\subsubsectionfont{\mdseries\upshape\bfseries\normalsize} % Set font options for subsubsections



\newenvironment{publist}{%
  \begin{list}{}{%
    \setlength{\leftmargin}{0cm}   % Adjust left margin here
    \setlength{\labelwidth}{2cm}     % Adjust label width here (for the year)
    \setlength{\labelsep}{0.5cm}     % Adjust space between label and text
  }%
}{%
  \end{list}%
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}


%sections
\titleformat
{\section} % command
[display] % shape
{\rmfamily \mdseries\large} % format
{\thesection} % label
{0.5ex} % sep
{
    %\rule{\textwidth}{1pt}
} % before-code
[
\rule{\textwidth}{0.3pt}
] % after-code


\titleformat{\subsection}
  {\normalfont\normalsize\itshape\bfseries}{\thesubsection.}{1em}{}


% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
\textbf{{\huge \name}}\\
\\
Last updated: \today

\vspace{5ex}


% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}
%\centerline{Last updated: \today}



\begin{minipage}{0.45\linewidth}
  Hamline University \\
  Criminal Justice \& Forensic Science \\
  306-A East Hall \\
 1556 Hewitt Ave \\
 St Paul, MN 55104
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Office: & (651) 523-2168 \\
    %Cell: &  (218) 244-7188 \\
    Email: & \href{mailto:rlarson21@hamline.edu}{rlarson21@hamline.edu} \\
    Web: & \href{https://ryanplarson.github.io/personal_site/}{ryanplarson.github.io} \\
   Twitter: &  \href{https://twitter.com/ryanplarson}{@ryanplarson} \\
  \end{tabular}
\end{minipage}



\section*{\textbf{Appointments}}


\begin{publist}

\item[\textbf{2022-present}] Assistant Professor of Criminology, Hamline University

\item[\textbf{2023-present}] Co-Director of the Summer Collaborative Undergraduate Research Program (SCUR), Hamline University


\end{publist}



\section*{\textbf{Education}}

\begin{publist}
  \item[\textbf{2022}] Ph.D. Sociology, University of Minnesota - Twin Cities
   \begin{itemize}
     %\item Advisor: \href{http://www.soc.umn.edu/~uggen/}{Chris Uggen}
	\item \textit{Committee:} Chris Uggen (Advisor),  Doug Hartmann, Ann Meier, Josh Page, Aaron Sojourner 
	%\item \textit{Preliminary Exam:} ``Bringing Crime Back In: Crime Etiology and Punishment Effects"
           \item \textit{Dissertation:} \href{https://conservancy.umn.edu/bitstream/handle/11299/243159/Larson_umn_0130E_23712.pdf?sequence=1}{The Iatrogenic Effects of Punishment}
\end{itemize}
    
\item[\textbf{2018}] M.A. Sociology, University of Minnesota - Twin Cities

\item[\textbf{2014}] B.A. Sociology and Psychology, Concordia College
 \begin{itemize}
     \item \textit{Honors}: \textit{Summa cum Laude}, 2014 Farden Memorial Prize in Sociology
    \end{itemize}
\end{publist}

\section*{\textbf{Areas of Interest}}

Crime, Punishment, and Stratification, Quantitative Methodology and Statistics, Spatial Analysis, Causal Inference


\section*{\textbf{Publications} \scriptsize{\textsuperscript{+} denotes student co-author}} 

\subsection*{Peer-Reviewed Articles}

\begin{publist}

\item[\textbf{2026}] \textbf{Larson, Ryan P.}, James Densley, Jillian Peterson, Jaycee Manchi\textsuperscript{+}, N. Jeanie Santaularia, Christopher Uggen, and Christopher E. Robertson\textsuperscript{+}. ``The Changing Nature of Homicide in the Twin Cities: 
An Interrupted Time Series Analysis of the Police Murder of George Floyd." Forthcoming at \textit{Journal of Quantitative Criminology}.

\item[\textbf{2025}]  Santaularia, N. Jeanie, \textbf{Ryan Larson}, Christopher E. Robertson\textsuperscript{+}, Christopher Uggen. \href{https://ryanplarson.github.io/personal_site/pubs/santaularia_etal_25_final.pdf}{``Mental Health Before and After George Floyd’s Murder in Minneapolis in Black, Latine, and White Communities."}\textit{American Journal of Epidemiology} 194(7): 1900-1908. 

\begin{itemize}
\item Media: \href{https://www.mprnews.org/story/2024/09/19/black-minneapolis-residents-bear-heaviest-mental-health-burden-after-george-floyds-murder}{\textit{Minnesota Public Radio}}
\end{itemize}

\item[\textbf{2024}] Schwendeman, Hannah\textsuperscript{+}, Veronica L. Horowitz, Frank Edwards, Robert Stewart, \textbf{Ryan Larson}, and Christopher Uggen. \href{https://ryanplarson.github.io/personal_site/pubs/schwendeman_etal_24.pdf}{``'It's Two Separate Systems That..Keep You Under a Thumb': Dual Debt in the Child Support and Criminal Legal Systems."} \textit{Law and Society Review} 58(4): 547-572. 

\item Lind, Allison\textsuperscript{+}, \textbf{Ryan P. Larson}, Susan M. Mason, and Christopher Uggen. \href{https://ryanplarson.github.io/personal_site/pubs/lind_etal_24.pdf}{``Carjacking and Homicide in Minneapolis After the Police Killing of George Floyd:  Evidence from an Interrupted Time Series Analysis."} \textit{Social Science \& Medicine} 358: 1-19.

\begin{itemize}
\item Winner of the 2023 American College of Epidemiology (ACE) Student Paper of the Year Award
\end{itemize}

\item Shannon, Sarah, \textbf{Ryan Larson}, Ian Kennedy,  Kate O'Neill, and Alexes Harris. \href{https://ryanplarson.github.io/personal_site/pubs/shannon_etal_24.pdf}{``Economic Extraction via the Criminal Legal System: A Community-level Perspective."} \textit{Socius} 10. 

\item Horowitz, Veronica, \textbf{Ryan P. Larson}, Robert Stewart, and Christopher Uggen. \href{https://ryanplarson.github.io/personal_site/pubs/horowitz_etal_24.pdf}{``Fines, Fees, and Families: Monetary Sanctions as Stigmatized Intergenerational Exchange."} \textit{The Sociological Quarterly} 1-20.

\item[\textbf{2023}] \textbf{Ryan P. Larson}, Jeanie Santaularia, and Christopher Uggen. \href{https://ryanplarson.github.io/personal_site/pubs/larson_etal_23_online.pdf}{``Temporal and Spatial Shifts in Gun Violence, Before and After a Historic Police Killing in Minneapolis."} \textit{Spatial and Spatiotemporal Epidemiology} 100602.

\item[\textbf{2022}] Horowitz, Veronica, Kimberly Spencer-Suarez, \textbf{Ryan Larson}, Robert Stewart, Frank Edwards, Emmi Obara, and Chris Uggen. \href{https://ryanplarson.github.io/personal_site/pubs/horowitz_etal_22.pdf}{``Dual Debtors: Child Support and Criminal Financial Legal Obligations."} \textit{Social Service Review}, 96(2): 226-267.

\item Horowitz, Veronica,  \textbf{Ryan Larson}, Victoria Piehowski, Allison Nobles, and Josh Page. \href{https://ryanplarson.github.io/personal_site/pubs/horowitz_etal_21.pdf}{``Pragmatic Punitiveness: The Institutionalization of Criminal Domestic Violence Protection Orders."} \textit{Social \& Legal Studies}, 31(5): 679-703.

\item Hamilton, Amber, Doug Hartmann, and \textbf{Ryan P. Larson}. \href{https://ryanplarson.github.io/personal_site/pubs/hamilton_etal_22.pdf}{``Assessing and Extending Colorblind Racism Theory Using National Survey Data."} \textit{Sociology of Race and Ethnicity}, 8(2): 267-283.

\item Stewart, Rob, Bieanna Watters, Veronica Horowitz, \textbf{Ryan Larson}, Brian Sargent, and Christopher Uggen. \href{https://ryanplarson.github.io/personal_site/pubs/stewart_etal_22.pdf}{``Native Americans and Monetary Sanctions."} \textit{The Russell Sage Foundation Journal of the Social Sciences}, 8(2) 137-156.

\begin{itemize}
\item Media: \href{https://www.mprnews.org/story/2022/04/21/native-women-incarcerated}{\textit{Minnesota Public Radio}}, \href{https://www.irp.wisc.edu/resource/brieanna-watters-and-robert-stewart-on-native-americans-and-monetary-sanctions/}{\textit{Institute for Research on Poverty (podcast)}}
\end{itemize}

\item[\textbf{2021}] \textbf{Larson, Ryan P.}, Chris Uggen, Sarah Shannon, and Aaron Sojourner. \href{https://ryanplarson.github.io/personal_site/pubs/larson_etal_22.pdf}{``Felony History and Change in U.S. Employment Rates."} \textit{Social Science Research} 103 102649.

\item  Santaularia, Jeanie, \textbf{Ryan P. Larson}, and Christopher Uggen. \href{https://ryanplarson.github.io/personal_site/pubs/santaularia_etal_21.pdf}{``Criminal Punishment and Violent Injury in Minnesota."} \textit{Injury Epidemiology}, 8(11) 1-10.

\item[\textbf{2019}] Stewart, Evan, Penny Edgell, Sarah-Catherine Billups, and \textbf{Ryan Larson}. \href{https://ryanplarson.github.io/personal_site/pubs/stewart_etal_19.pdf}{``The Stakes of Symbolic Boundaries."} \textit{The Sociological Quarterly}, 61(2): 309-333.

\item[\textbf{2018}] Meier, Ann, Ben Hartmann\textsuperscript{+}, and \textbf{Ryan Larson}.  \href{https://ryanplarson.github.io/personal_site/pubs/meier_etal_18.pdf}{``A Quarter Century of Youth Activity Participation: Inequalities by Race, Class, Gender and Age?"}. \textit{Journal of Youth and Adolescence} 47(6): 1299-1316.

\item \textbf{Larson, Ryan P.} and Andrew Lindner. \href{https://ryanplarson.github.io/personal_site/pubs/larson_lindner_18.pdf}{``Professionalization Through Attrition?: An Event History Analysis of Mortalities in Citizen Journalism."}  \textit{Information, Communication, and Society} 21(5): 746-760.

\item[\textbf{2017}] Lindner, Andrew and \textbf{Ryan P. Larson}. \href{https://ryanplarson.github.io/personal_site/pubs/lindner_larson_17.pdf}{``The Expansion and Contraction of the Journalistic Field and American Online Citizen Journalism, 2000-2012"}. \textit{Poetics} 64: 40-52.

\item Hartmann, Doug, Paul Croll, \textbf{Ryan Larson}, Joseph Gerteis, and  Alex Manning. \href{https://ryanplarson.github.io/personal_site/pubs/hartmann_etal_17.pdf}{``Colorblindness as Identity:  Key Determinants, Relations to Ideology, and Implications for Attitudes about Race and Policy"}. \textit{Sociological Perspectives} 60(5): 866-888.

\item[\textbf{2015}] Hawkins, Daniel, Andrew Lindner, \textbf{Ryan Larson}, and Johnathan Santos. \href{https://ryanplarson.github.io/personal_site/pubs/hawkins_etal_15.pdf}{``Overrating Bruins, Underrating Badgers: Media, Prestige, and College Basketball Rankings."} \textit{Journal of Sports Management and Commercialization} 6(3): 11-26.

\end{publist}

\subsection*{Book Chapters}

\begin{publist}

\item[\textbf{2023}] Christopher Uggen, \textbf{Ryan Larson}, Sarah Shannon, Robert Stewart, and Caleigh Lueder\textsuperscript{+}. \href{https://ryanplarson.github.io/personal_site/pubs/uggen_etal_23.pdf}{``The Denial of Voting Rights to People with Criminal Records."} \textit{Social Problems in an Age of Mass Incarceration}. Edited by Kristen M. Budd, David Lane, Glenn Muschert, and Jason Smith. Society for the Study of Social Problems (SSSP).

\item[\textbf{2020}] \textbf{Larson, Ryan P}. \href{https://ryanplarson.github.io/personal_site/pubs/larson_19.pdf}{``Felon Disenfranchisement."} \textit{Voting and Political Representation in America: Issues and Trends}, edited by Mark P. Jones. Santa Barbara, CA: ABC-CLIO.

\item[\textbf{2018}] Lindner, Andrew, and \textbf{Ryan P. Larson}. \href{https://ryanplarson.github.io/personal_site/pubs/lindner_larson_18.pdf}{``Regression Analysis."} \textit{Encyclopedia of Sociology}, edited by George Ritzer. Oxford: Wiley-Blackwell.

\item[\textbf{2017}] \textbf{Larson, Ryan P.} and Chris Uggen. \href{https://ryanplarson.github.io/personal_site/pubs/uggen_larson_17.pdf}{``Felon Disenfranchisement."} \textit{Encyclopedia of Corrections}, edited by Kent R. Kerley. Oxford: Wiley-Blackwell.

\end{publist}


\subsection*{Technical Reports and Other Writing}

\begin{publist}

\item[\textbf{2024}] Uggen, Christopher, \textbf{Ryan Larson}, Sarah Shannon, Robert Stewart, and Molly Hauf\textsuperscript{+}. \href{https://www.sentencingproject.org/app/uploads/2024/10/Locked-Out-2024-Four-Million-Denied-Voting-Rights-Due-to-a-Felony-Conviction.pdf}{``Locked Out 2024: Four Million Denied Voting Rights Due to a Felony Conviction."} Washington, D.C.: The Sentencing Project.

\begin{itemize}

\item Selected Media: \href{https://www.nytimes.com/live/2024/10/15/opinion/thepoint?smid=url-share}{\textit{The New York Times}}, \href{https://apnews.com/article/conviction-register-vote-incarcerated-georgia-sentencing-project-706e6e779125976302bec47ae08a6c53}{\textit{Associated Press}}, \href{https://www.newsweek.com/map-shows-voting-rights-felons-1977573}{\textit{Newsweek}}, \href{https://www.tennessean.com/story/news/2024/10/10/tn-has-highest-felony-disenfranchisement-rate-in-nation-report-finds/75597410007/}{\textit{The Tennesseean}}, \href{https://coloradonewsline.com/2024/10/10/coloradans-disenfranchised-while-imprisoned-felonies/}{\textit{Colorado Newsline}}, \href{https://news.yahoo.com/news/one-13-tennessee-adults-cant-142601002.html}{\textit{Yahoo! News}}, \href{https://www.commondreams.org/news/4-million-voters-felony-disenfranchisement}{\textit{Common Dreams}}, \href{https://www.phillyvoice.com/voter-disenfranchisement-pennsylvania-incarceration-report/}{\textit{Philly Voice}}, \href{https://www.dailymail.co.uk/wires/ap/article-13944251/Advocates-Georgia-face-barriers-getting-people-incarcerated-vote.html}{\textit{Daily Mail}}, \href{https://www.ncja.org/crimeandjusticenews/defying-national-trends-people-with-convictions-face-steep-voting-barriers-in-georgia}{\textit{National Criminal Justice Association}}, \href{https://www.independent.co.uk/news/georgia-ap-atlanta-donald-trump-people-b2626923.html}{\textit{The Independent}}, \href{https://abcnews.go.com/Politics/wireStory/nebraska-high-court-decide-residents-felony-records-vote-114842611}{\textit{ABC News}}, \href{https://www.osce.org/files/f/documents/4/1/579187.pdf}{\textit{Organization for Security and Co-operation in Europe Office for Democratic Institutions and Human Rights Interim Report October 2024}}, \href{https://www.stuttgarter-zeitung.de/inhalt.us-wahl-warum-vier-millionen-amerikaner-nicht-waehlen-duerfen.c04b5a9c-d543-4116-861a-3680ed956b2d.html}{\textit{Stuttgarter Zeitung}}, \href{https://atlanta.capitalbnews.org/restored-voting-rights-election-2024/}{\textit{CapitalB}}

\end{itemize}

\item[\textbf{2023}] Remington, Katie, \textbf{Ryan Larson}, and Molly Hauf\textsuperscript{+}. ``The Status Quo of Financial-Based Driver's License Suspensions in Minnesota." Forthcoming from the \textit{Minnesota Justice Research Center}.

\item[\textbf{2022}] Uggen, Christopher, \textbf{Ryan Larson}, Sarah Shannon, and Robert Stewart. \href{https://www.sentencingproject.org/app/uploads/2024/02/Locked-Out-2022-Estimates-of-People-Denied-Voting.pdf}{``Locked Out 2022: Estimates of People Denied Voting Rights Due to a Felony Conviction."} Washington, D.C.: The Sentencing Project.

\begin{itemize}
\item Media:  \href{https://www.nytimes.com/2024/09/09/opinion/tennessee-voter-felony-convictions.html}{\textit{The New York Times}}, \href{https://www.npr.org/2022/10/25/1130622918/felon-voting-state-laws-disenfranchisement-rates}{\textit{National Public Radio}}, \href{https://www.independent.co.uk/news/world/americas/us-politics/felony-voting-rights-florida-law-b2210267.html}{\textit{The Independent}}, \href{https://thehill.com/homenews/campaign/3703486-4-6-million-ineligible-to-vote-due-to-felony-convictions/}{\textit{The Hill}}, \href{https://www.themarshallproject.org/2022/11/04/florida-s-voter-fraud-arrests-are-scaring-away-formerly-incarcerated-voters}{\textit{The Marshall Project}}, \href{https://www.washingtoninformer.com/locked-out-millions-of-voters-are-disenfranchised-ahead-of-midterm-elections/}{\textit{The Washington Informer}}, \href{https://www.nationofchange.org/2022/10/28/the-sentencing-project-reports-4-6-million-americans-barred-from-voting-in-2022-midterms-because-of-felony-conviction/}{\textit{Nation of Change}}, \href{https://sacobserver.com/2022/10/locked-out-millions-of-voters-are-disenfranchised-ahead-of-midterm-elections/}{\textit{The Sacramento Observer}}, \href{https://www.davisvanguard.org/2022/10/report-no-voting-rights-for-4-6-million-americans-with-felony-convictions/}{\textit{The Davis Vanguard}}, \href{https://daily.jstor.org/voting-rights-for-people-convicted-of-felonies/}{\textit{JSTOR Daily}}, \href{https://www.newsweek.com/millions-americans-will-left-behind-upcoming-midterms-opinion-1756177}{\textit{Newsweek}}, \href{https://tntribune.com/locked-out-millions-of-voters-are-disenfranchised-ahead-of-midterm-elections/}{\textit{The Tennessee Tribune}}, \href{https://www.propublica.org/article/tennessee-black-voters-disenfranchised}{\textit{ProPublica}}, \href{https://communityjournal.net/locked-out-millions-of-voters-are-disenfranchised-ahead-of-midterm-elections/}{\textit{Milwaukee Community Journal}},  \href{https://www.abqjournal.com/2546427/new-report-shines-light-on-17k-new-mexicans-not-allowed-to-vote.html}{\textit{Albuquerque Journal}}, \href{https://www.buzzfeednews.com/article/skbaer/florida-felons-voter-fraud-disenfranchisement}{\textit{Buzzfeed News}},  \href{https://wpln.org/post/hundreds-of-thousands-of-tennesseans-cant-vote-because-of-a-felony-conviction-they-are-challenging-state-law-to-have-their-voices-heard/}{\textit{WPLN News}}, \href{https://sourcenm.com/2022/10/27/over-17000-new-mexicans-barred-from-voting-in-the-midterms-report-shows/}{\textit{Source NM}}, \href{https://journalistsresource.org/criminal-justice/felony-disenfranchisement-explainer-research-roundup/}{\textit{Journalist's Resource}}. \href{https://www.usatoday.com/story/opinion/columnist/2024/09/30/trump-felony-conviction-voting-rights/75339894007/}{\textit{USA Today}}, \href{https://wisconsinwatch.org/2024/10/wisconsin-voting-rights-felonies-election-incarcerated-probation-parole/}{\textit{Wisconsin Watch}}, \href{https://www.detroitnews.com/story/opinion/2024/10/15/kinloch-congress-must-work-to-protect-voting-rights/75686221007/
}{\textit{Detroit News}}
\end{itemize}

\item[\textbf{2020}] Uggen, Christopher, \textbf{Ryan Larson}, Sarah Shannon, and Arleth Pulido-Nava\textsuperscript{+}. \href{https://www.sentencingproject.org/publications/locked-out-2020-estimates-of-people-denied-voting-rights-due-to-a-felony-conviction/}{``Locked Out 2020: Estimates of People Denied Voting Rights Due to a Felony Conviction."} Washington, D.C.: The Sentencing Project.
\begin{itemize}
\item Media: \href{https://www.nytimes.com/live/2020/10/18/us/trump-vs-biden}{\textit{The New York Times}}, \href{https://www.vox.com/2020/10/14/21515850/voting-rights-sentencing-project-felon-disenfranchisement}{\textit{Vox}}, \href{https://www.cnn.com/2020/10/15/us/felony-convictions-voting-sentencing-project-study/index.html}{\textit{CNN}}, \href{https://www.buzzfeednews.com/article/skbaer/millions-cant-vote-2020-election-felony-convictions}{\textit{Buzzfeed}},  \href{https://apnews.com/article/election-2020-race-and-ethnicity-voting-rights-elections-tennessee-1467837105617bfd351b7b9969dc1683}{\textit{The Associated Press}}, \href{https://thehill.com/opinion/campaign/527510-thousands-of-people-with-felony-convictions-wont-be-able-to-vote-in-ga-run}{\textit{The Hill}}, \href{https://www.forbes.com/sites/joewalsh/2020/10/14/over-5-million-americans-wont-be-able-to-vote-next-month-because-of-criminal-records/?sh=3d0984982fc5}{\textit{Forbes}}, \href{https://www.epi.org/publication/rooted-racism-voter-suppression/#epi-toc-12}{Economic Policy Institute}
\end{itemize}

\item[\textbf{2017}] Uggen, Christopher and \textbf{Ryan P. Larson}. \href{https://ryanplarson.github.io/personal_site/pubs/uggen_larson_contexts_17.pdf}{``Is The Public Getting Smarter on Crime?"} \textit{Contexts Fall 2017}.

\item[\textbf{2016}] Uggen, Christopher, \textbf{Ryan Larson}, and Sarah Shannon. \href{http://www.sentencingproject.org/wp-content/uploads/2016/10/6-Million-Lost-Voters.pdf}{``6 Million Lost Voters: State-Level Estimates of Felony Disenfranchisement, 2016."} Washington, D.C.: The Sentencing Project.
\begin{itemize}
\item Winner of the 2018 ASA Section on Sociological Practice and Public Sociology's Publication Award
\item Selected Media Coverage: \href{http://www.nytimes.com/interactive/2016/10/06/us/unequal-effect-of-laws-that-block-felons-from-voting.html?_r=0}{\textit{The New York Times}}, \href{https://www.washingtonpost.com/news/powerpost/wp/2016/10/07/6-million-citizens-including-1-in-13-african-americans-are-blocked-from-voting-because-of-felonies/}{\textit{The Washington Post}}, \href{http://www.huffingtonpost.com/harlan-green/trump-the-terrible-demago_b_12392904.html}{\textit{The Huffington Post}}, \href{http://www.vogue.com/13489654/2016-presidential-election-felony-disenfranchisement/}{\textit{Vogue}}, \href{http://www.rollingstone.com/politics/features/six-million-adults-who-wont-influence-this-election-w443693}{\textit{Rolling Stone}}, \href{https://www.yahoo.com/news/more-6-million-americans-t-vote-election-105300558.html}{\textit{Yahoo! News}}, \href{https://www.youtube.com/watch?time_continue=2&v=NpPyLcQ2vdI}{\textit{Last Week Tonight with John Oliver}}, \href{https://www.bet.com/article/0g0u0z/the-impact-of-felony-disenfranchisement-on-black-communities-a-deep-dive-into-modern-day-voter-suppression}{BET}
\end{itemize}

\item[\textbf{2016}] Lindner, Andrew and \textbf{Ryan P. Larson}. \href{http://journals.sagepub.com/doi/full/10.1177/1536504216685127}{``The Year English Soccer Wasn't For Sale."} \textit{Contexts Fall 2016}. 

\end{publist}


\section*{\textbf{Works in Progress} \scriptsize{\textsuperscript{+} denotes student co-author}}

\subsection*{Manuscripts Under Review}
\begin{publist}

\item \textbf{Ryan P. Larson}, Robert Stewart, Veronica Horowitz, and Christopher Uggen. ``The Racialized Packaging of Punishment: An Instrumental Variables Approach to Confinement, Surveillance, and Financial Extraction." Revise and resubmit at \textit{Criminology}.

\item Maryam Tanveer\textsuperscript{+}, \textbf{Ryan Larson}, N. Jeanie Santaularia, Christopher Robertson\textsuperscript{+}, and Christopher Uggen. ``Temporal Exposure to Police-Involved Shootings and the Incidence of Mental Health Conditions in Minneapolis, Minnesota." Revise and resubmit at \textit{Journal of Urban Health}.

\item \textbf{Ryan P. Larson}. ``The Causal Packaging Effects of Punishment". Under review at \textit{Social Science Research}.

\item Christopher Uggen, Carsyn Schneider\textsuperscript{+}, \textbf{Ryan Larson}, and Robert Stewart. ``Democratic Expansion? Restoring the Vote to People on Probation and Parole in the United States, 1964-2023." Under review at \textit{Criminology \& Public Policy}.


\end{publist}

\subsection*{Working Papers}
\begin{publist}

\item Christopher Uggen, \textbf{Ryan Larson}, Robert Stewart, Frank Edwards, Veronica Horowitz, and Hannah Schwendeman\textsuperscript{+}. ``How Monetary Sanctions and Child Support Affect Children's Educational Outcomes and Residential Stability."

\item Kennedy, Ian, Kate K. O’Neill, Alexes Harris, \textbf{Ryan Larson}, and Sarah Shannon. “A National Perspective on Debtors’ Blocks: How Racialized LFO Burden Disrupts Neighborhood Success”.

\item \textbf{Ryan Larson}, Molly Hauf\textsuperscript{+}, Christopher Uggen, Sarah Shannon, and Robert Stewart. ``Locked Out, Broken Down: State-Level Estimates of Felony Disenfranchisement by Gender."

\item \textbf{Ryan P. Larson}. ``Ban-the-Box, Employment, and Crime". 

\item \textbf{Ryan Larson}, Iris Fuglie\textsuperscript{+}, Andrew Lindner, and Christopher Uggen. ``Contested Citizenship: Race, Framing, and Public Support for Felony Disenfranchisement."

\item \textbf{Ryan P. Larson}. ``Punishment, Neighborhood Structure, and Crime".

\item \textbf{Larson, Ryan}, Jeanie Santaularia, Chris Robertson\textsuperscript{+}, Ryan LeCount, and Chris Uggen.  ``Patterns of Support in Minneapolis’ Police Charter Amendment." 

%\item \textbf{Ryan P. Larson}, Veronica Horowitz, Robert Stewart, and Christopher Uggen. ``Multiplicative Debt: Legal Financial Obligations and Child Support Arrears."

%\item \textbf{Ryan P. Larson}, Veronica Horowitz, Robert Stewart, and Christopher Uggen. ``The Criminogenic Essence of Dual Debt."

%\item \textbf{Ryan Larson},  Chris Uggen, Rob Stewart, and Veronica Horowitz. ``The Effects of Monetary Sanctions on Recidivism: Evidence from Quasi-Random Judge Assignment in Minnesota."

%\item Uggen, C., \textbf{Larson, R.}, Curry, C., \& Reynoso, N. O. 2022. ``How housing and education interventions shape justice system involvement: Evidence from Minnesota."


\end{publist}

\section*{\textbf{Grants, Awards, \& Honors}}

\begin{publist}

\item[\textbf{2025}] Fund for a Safer Future. \textit{Structural Racism, Police Shootings, and Public Health}. [Co-PI with N. Jeanie Santaularia]. Under Review. 

\item Hamline University Ridgway Summer Collaborative Undergraduate Research (SCUR) Award w/ Iris Fuglie (\$6,000).

\item[\textbf{2024-2025}] Arnold Ventures. "Research Support for Minnesota Sentencing Guidelines Comission: Comprehensive Review of Minnesota's Sentencing System." [Co-I with Robert Stewart and Co-PI Christopher Uggen]. \$996,137. 

\item[\textbf{2024}] The Sentencing Project. “Felon Disenfranchisement Research Support.” [Co-PI with Christopher Uggen, Sarah Shannon, and Robert Stewart]. 10/1/23-10/1/24. \$25,000.

\item[\textbf{2023}] Hamline University Ridgway Summer Collaborative Undergraduate Research (SCUR) Award w/ Molly Hauf (\$6,000).

\item[\textbf{2022}]The Sentencing Project. “Felon Disenfranchisement Research Support.” [co-PI with Christopher Uggen, Sarah Shannon, and Robert Stewart]. 10/1/21-10/1/22. \$8,000.

\item[\textbf{2021-2024}]  Laura and John Arnold Foundation. ``\textit{Dual Debt: Understanding the Relationship between Legal Financial Obligations and Child Support Debt.}" [Co-Is with Robert Stewart, Veronica Horowitz, Kimberly Spencer-Suarez, Frank Edwards, and PI Chris Uggen]. Part of ``\textit{Monetary Sanctions Collective: Understanding the Broader Reach and Burden of Monetary Sanctions.}" 10/1/21-9/30/24. \$1,745,816 (\$486,025 on Dual Debt project).

\item[\textbf{2021}] Professional Development Award. Department of Sociology, University of Minnesota. 

\item[\textbf{2020}] The Sentencing Project. “Felon Disenfranchisement Research Support.” [co-PI with Christopher Uggen, and Sarah Shannon]. 10/1/19-10/1/20. \$8,000.

\item[\textbf{2018}] Professional Development Award. Department of Sociology, University of Minnesota. 
\item[\textbf{2017}] Professional Development Award. Department of Sociology, University of Minnesota. 
\item[\textbf{2016}] The Sentencing Project. “Felon Disenfranchisement Research Support.” [co-PI with Christopher Uggen, and Sarah Shannon]. 10/1/15-10/1/16. \$8,000.
\item American Mosaic Project (AMP) Graduate Research Fellowship (\$5000). Department of Sociology, University of Minnesota
\item Professional Development Award. Department of Sociology, University of Minnesota. 
\item[\textbf{2015}] American Mosaic Project (AMP) Graduate Research Fellowship (\$5000). Department of Sociology, University of Minnesota. 
\item National Science Foundation Graduate Research Fellowship Honorable Mention
\item Professional Development Award. Department of Sociology, University of Minnesota. 
\item[\textbf{2014}]Farden Memorial Prize in Sociology Winner. Concordia College Department of Sociology and Social Work, Concordia College
\item Midwest Sociological Society Student Paper Competition Second Place Winner,  ``Fear and Loathing in Minnesota: A Multilevel Analysis of Factors Influencing Crime Fears"
\item[\textbf{2013}] Student Scholar Grant Recipient, Concordia College (\$500)
\item[\textbf{2010}] Presidential Scholarship Recipient, Concordia College

\end{publist}



\section*{\textbf{Academic Presentations} \scriptsize{\textsuperscript{+} denotes student co-presenter}} 

\begin{publist}

\item [\textbf{2026}] Veronica Horowitz, Ryan Larson, Robert Stewart, and Christopher Uggen. ``The Package is the Punishment: Unpacking combinations of punishment from different methodologies" Accepted for presentation at the 2026 Law and Society Association Annual Meeting 2026, San Francisco, CA. 

\item [\textbf{2025}] Ian Kennedy, Kate K. O'Neill, \textbf{Ryan Larson}, Hannah Lee, Sarah Shannon, and Alexes Harris. ``A Racial Capitalist Perspective on Debt Blocks: The State-Run Extraction of Wealth and Resources from Debt-Burdened Neighborhoods." Presented at the Population Association of America Annual Meeting 2025, Washington, D.C. 

\item Veronica Horowitz, Brittany Martin, Andrea Guiffre, \textbf{Ryan Larson}, Robert Stewart, Christopher Uggen, and Alexes Harris. ``The Multiplicities of Punishment." Accepted for presentation at the 2025 American Society of Criminology Annual Conference, Washington, D.C. 

\item Molly Hauf\textsuperscript{+} \textbf{Ryan Larson}, Sarah Shannon, Robert Stewart, and Ryan Larson. ``Locked Out, Broken Down: Gender-Specific Estimates of State Variation in Felon Disenfranchisement." Accepted for presentation at the 2025 American Society of Criminology Annual Conference, Washington, D.C. 

\item \textbf{Ryan Larson}, Christopher Uggen, Robert Stewart, and Veronica Horowitz. ``The Racialized Packaging of Punishment: A Mixture Model Approach." Accepted for presentation at the 2025 American Society of Criminology Annual Conference, Washington, D.C. 

\item \textbf{Ryan Larson}. ``Understanding \textit{Locked Out}" Invited Panelist for \textit{The Sentencing Project's} Civic Power 2025 Convening in Chicago, IL. 

\item Christopher Uggen, \textbf{Ryan Larson}, Robert Stewart, Frank Edwards, Veronica Horowitz, and Hannah Schwendeman\textsuperscript{+}. ``How Monetary Sanctions and Child Support Affect Children's Educational Outcomes and Residential Stability." Submitted for presentation at the 2025 American Sociological Association Annual Conference, Chicago, IL. 

\item Ryan Larson. ``Disenfranchisement in the 2020's". Invited CwC panelist for the Southern Political Science Association Annual Conference, Puerto Rico. 

\item[\textbf{2024}] Maryam Tanveer\textsuperscript{+}, \textbf{Ryan Larson}, N. Jeanie Santaularia, Christopher Robertson\textsuperscript{+}, and Christopher Uggen. ``Temporal Exposure to Police-Involved Shootings and the Incidence of Mental Health Conditions in Minneapolis, Minnesota." Presented at the 2024 National Research Conference for the Prevention of Firearm-Related Harms, Seattle, WA. 

\item \textbf{Larson, Ryan}. ``Crime Etiology, Punishment, and Local Crime Trends." Invited talk for the October 2024 Hennepin County District Judges Education Committee.  

\item Jillian Peterson, James Densley, \textbf{Ryan Larson}, Jaycee Manchi\textsuperscript{+}, N. Jeanie Santaularia, Christopher Uggen, and Christopher E. Robertson\textsuperscript{+}. "The Changing Nature of Homicide in the Twin Cities Before, During, and After the Pandemic and the Murder of George Floyd." Presented at the 2024 American Society of Criminology Annual Conference, San Francisco, CA. 

\item \textbf{Larson, Ryan}. ``Punishment, Neighborhood Structure, and Crime." Presented at the 2024 American Society of Criminology Annual Conference, San Francisco, CA. 

\item Christopher Uggen, \textbf{Ryan Larson}, Robert Stewart, Frank Edwards, Veronica Horowitz, and Hannah Schwendeman\textsuperscript{+}. ``How Monetary Sanctions and Child Support Affect Children's Educational Outcomes and Residential Stability." Presented at the 2024 American Society of Criminology Annual Conference, San Francisco, CA. 

\item Veronica Horowitz, Makaela Brass\textsuperscript{+}, Hannah Schwendeman\textsuperscript{+}, Rob Stewart, \textbf{Ryan Larson}, and Christopher Uggen. ``Tell Her To Go Get a Job!': Gendered Attitudes Among Men with Dual Debt." Presented at the 2024 American Society of Criminology Annual Conference, San Francisco, CA. 

\item Kennedy, Ian, Kate K. O’Neill, Alexes Harris, \textbf{Ryan Larson}, and Sarah Shannon. ``A National Perspective on Debtors’ Blocks: How Racialized LFO Burden Disrupts Neighborhood Success." Presented at the 2024 American Sociological Association Annual Conference, Montreal, CA. 

\item Christopher Uggen, Carsyn Schneider\textsuperscript{+}, \textbf{Ryan Larson}, and Robert Stewart. ``Democratic Expansion? Restoring the Vote to People on Probation and Parole in the United States, 1964-2023." Presented at the 2024 American Sociological Association Annual Conference, Montreal, CA. 

\item Molly Hauf\textsuperscript{+} and \textbf{Ryan Larson}. ``Locked Out, Broken Down: Gender-Specific Estimates of State Variation in Felon Disenfranchisement." Presented at the Minnesota Private College Council's \textit{Scholars at the Capitol} Event, St. Paul, MN. 

\item Molly Hauf\textsuperscript{+} and \textbf{Ryan Larson}. ``Locked Out, Broken Down: Gender-Specific Estimates of State Variation in Felon Disenfranchisement." Presented at the 2024 National Conference for Undergraduate Research, Long Beach, CA. 

\item Christopher Uggen, Carsyn Schneider\textsuperscript{+}, \textbf{Ryan Larson}, Robert Stewart. ``Democratic Expansion? Restoring the Vote to People on Probation and Parole in the United States, 1964-2023". Presented at the 2024 Law \& Society Association Annual Conference, Denver, CO. 

\item Schwendeman, Hannah, Veronica L. Horowitz, Robert Stewart, \textbf{Ryan Larson}, Frank Edwards, and Christopher Uggen. 2024.  ``Theorizing Legal Cynicism, Legal Estrangement, and System Avoidance: Dual Debt in the Child Support and Criminal Legal Systems." Presented at the 2024 Law \& Society Association Annual Conference, Denver, CO. 

\item Molly Hauf\textsuperscript{+} and \textbf{Ryan Larson}. ``Locked Out, Broken Down: Gender-Specific Estimates of State Variation in Felon Disenfranchisement." Presented at the Midwest Sociological Society 2024 Conference, Des Moines, IA. 

\item Molly Hauf\textsuperscript{+} and \textbf{Ryan Larson}. ``Locked Out, Broken Down: Gender-Specific Estimates of State Variation in Felon Disenfranchisement." Presented at the Hamline Interdisciplinary Student Research \& Creative Inquiry Symposium, St. Paul, MN. 

\item[\textbf{2023}] \textbf{Ryan P. Larson}, Christopher Robertson\textsuperscript{+}, and Kamisha Johnson. ``Tracing The Public Health Consequences of the Police Murder of George Floyd." Presented at the \textit{Minnesota Justice Research Center} 2023 Conference, Re-Imagining Justice: Centering Humanity Over Fear, Minneapolis, MN.   

\item \textbf{Ryan P. Larson}, Veronica Horowitz, Robert Stewart, and Christopher Uggen. ``The Criminogenic Essence of Dual Debt." Presented at the American Society of Criminology Annual Meeting, Philadelphia, PA. 

\item Schwendeman, Hannah, Veronica L. Horowitz, Robert Stewart, \textbf{Ryan Larson}, Frank Edwards, and Christopher Uggen. ``My Right Arm Should be ‘Debt’ and My Left Arm Should be ‘Felony’”:
Dual Debt in the Child Support and Criminal Legal Systems". Presented at the American Society of Criminology Annual Meeting 2023, Philadelphia, PA. 

\item \textbf{Ryan P. Larson}. ``Ban-the-Box, Employment, and Crime". Presented at the American Society of Criminology Annual Meeting 2023, Philadelphia, PA. 

\item Schwendeman, Hannah\textsuperscript{+}, Veronica L. Horowitz, Robert Stewart, \textbf{Ryan Larson}, Frank Edwards, and Christopher Uggen. ``My Right Arm Should be ‘Debt’ and My Left Arm Should be ‘Felony’”:
Dual Debt in the Child Support and Criminal Legal Systems". Presented at the American Sociological Association Annual Meeting 2023, Philadelphia, PA. 

\item N. Jeanie Santaularia, \textbf{Ryan Larson}, Christopher E. Robertson\textsuperscript{+}, Christopher Uggen. ``The Mental Health Consequences Before and After a Historic Police Killing in Minneapolis in Black and White Communities." Presented at the Society for Epidemiologic Research Annual Meeting 2023, Portland, OR.

\item \textbf{Larson, Ryan}. ``Punishment, Neighborhood Structure, and Crime." Presented at the 2023 Midwest Sociological Association Annual Meeting, Minneapolis, MN. 

\item \textbf{Larson, Ryan} and Ryan LeCount. ``Patterns of Support in Minneapolis’ Police Charter Amendment." Presented at the 2023 Midwest Sociological Association Annual Meeting, Minneapolis, MN. 

\item Allison Lind\textsuperscript{+}, \textbf{Ryan Larson}, Susan Mason, and Christopher Uggen. ``A Spatio-Temporal Analysis of Carjackings and Neighborhood Disadvantage: Implications for Population Health." Poster presentation at the 2023 Population Association Annual Meeting, New Orleans, LA. 

\item[\textbf{2022}] Horowitz, Veronica, \textbf{Ryan Larson}, Robert Stewart, and Chris Uggen. ``Monetary Sanctions Across 3 Generations." Presented at the 2022 American Sociological Association Annual Meeting, Los Angeles, CA. 

\item[\textbf{2021}] \textbf{Larson, Ryan}. ``The Causal Packaging Effects of Punishment." Presented at the American Society of Criminology Annual Meeting 2021, Chicago, IL. 

\item \textbf{Larson, Ryan}, Christopher Uggen, Robert Stewart, Veronica Horowitz. ``The Effects of Monetary Sanctions on Recidivism." Presented at the American Society of Criminology Annual Meeting 2021, Chicago, IL. 

\item Anna DalCorvito, \textbf{Ryan Larson}, Chris Uggen. ``Marginalization and Youth Decarceration in the United States, 2000-2018." Presented at the American Society of Criminology Annual Meeting 2021, Chicago, IL. 

\item Horowitz, Veronica, \textbf{Ryan P Larson}, Robert Stewart, and Chris Uggen. ``Gender and the Intergenerational Exchange of Monetary Sanctions." Presented at the American Society of Criminology Annual Meeting 2021, Chicago, IL. 

\item \textbf{Larson, Ryan}, Christopher Uggen, Robert Stewart, Veronica Horowitz. ``Race and the Packaging of Punishment: A Instrumental Variables Approach to Extra-Legal Sentencing Effects." Presented at the 2021 American Sociological Association Annual Meeting, virtual meeting. 

\item[\textbf{2020}] \textbf{Ryan P. Larson}, Jeanie Santaularia, Christopher Uggen. ``Criminal Punishment, Child Abuse, and Violent Injury in Minnesota, 2010-2014." Accepted for presentation at the 2020 American Society of Criminology Annual Meeting, Washington, D.C., cancelled due to COVID-19.  

\item \textbf{Larson, Ryan}, Christopher Uggen, Robert Stewart, Veronica Horowitz. ``The Racialized Packaging of Punishment: An Instrumental Variables Approach to Monetary Sanctions and Confinement." Accepted for presentation at the 2020 American Sociological Association Annual Meeting, San Francisco, cancelled due to COVID-19. 

\item \textbf{Larson, Ryan}, Chris Uggen, Sarah Shannon, and Aaron Sojourner. ``Former Felons and the Decline in U.S. Labor Force Participation, 1980-2010." Accepted for presentation at the 2020 Population Association of America Annual Meeting, Washington D.C, cancelled due to COVID-19. 

\item Spencer-Suarez, Kimberly, Robert Stewart, Veronica L. Horowitz, Emmi Obara, Frank Edwards, \textbf{Ryan Larson}, and Christopher Uggen. ``Dual Debtors: Navigating Child Support Arrears and Criminal Justice Debt." Society for Social Work and Research Annual Meetings, Washington, D.C.. January.

\item[\textbf{2019}] \textbf{Larson, Ryan}, Robert Stewart, Veronica Horowitz, and Christopher Uggen. ``The Socio-Cultural Effects of Race and Indigeneity on Monetary Sanctions in Minnesota." Invited panel at the 2019 American Society of Criminology Annual Meeting, San Francisco, CA.

\item[\textbf{2018}] \textbf{Larson, Ryan}, Chris Uggen, Sarah Shannon, and Aaron Sojourner. ``Former Felons and the Decline in U.S. Labor Force Participation, 1980-2010." Presented at the 2018 American Society of Criminology Annual Meeting, Atlanta, GA. 
\item Horowitz, Veronica, \textbf{Ryan P. Larson}, Allison Nobles, Victoria Piehowski, and Josh Page. ``No Contact: The Origins and Trajectory of Domestic Abuse Law in Minnesota." Presented at the 2018 Midwestern Sociological Society Annual Meeting, Minneapolis, MN. 

\item \textbf{Larson Ryan P.} and Doug Hartmann. ``Is Colorblindness Aspirational? Findings from a National Survey." Presented at the Midwestern Sociological Society Annual Meeting, Minneapolis, MN. 

\item Hamilton, Amber, Doug Hartmann, and \textbf{Ryan P. Larson}. ``An Analysis of Racial Variation in Colorblind Racism." Presented at the Midwestern Sociological Society Annual Meeting, Minneapolis, MN. 

\item[\textbf{2017}] Hartmann, Doug and \textbf{Ryan P. Larson}. ``What is it about Sport? Rethinking Data and Measurement in the Analysis of Participation Effects."  Presented at the North American Society for the Sociology of Sport Annual Conference, Windsor, Ontario, CA. 

\item \textbf{Larson, Ryan} and Andrew Lindner. ``The Mortality of Citizen Journalism Sites: An Event History Analysis." Presented at the American Sociological Association Annual Meeting, Montreal, QC, CA.

\item[\textbf{2016}] \textbf{Larson, Ryan} and Chris Uggen. ``A Competing Risk Analysis of Immigrant Detention and Case Outcomes." Presented at the American Society of Criminology Annual Meeting, New Orleans, LA. 

\item \textbf{Larson, Ryan}. ``Mapping Youth Activities in the Twin-Cities Metro Area." Presented at the 2016 University of Minnesota Sociology Research Institute, Minneapolis, MN. 

\item \textbf{Larson, Ryan}, Jacqui Frost, and Stephen Wulff. ``The Good, The Bad, and The Ugly: Syllabus Composition." Presented at the 2016 University of Minnesota Sociology Research Institute, Minneapolis, MN. 

\item Hartmann, Doug, \textbf{Ryan Larson}, Paul Croll, Alex Manning,  and Joseph Gerteis. ``Colorblindness as Identity:  Key Determinants, Relations to Ideology, and Implications for Attitudes about Race and Policy". Presented at the Midwestern Sociological Society Annual Meeting, Chicago, IL. 

\item Meier, Ann, Ben Hartmann, and \textbf{Ryan Larson}. ``25 Years of Youth Activity Participation: Inequalities by Race, Class, and Gender?". Presented at the Midwestern Sociological Society Annual Meeting, Chicago, IL. 

\item[\textbf{2015}] Hawkins, Daniel, Andrew M. Lindner, and \textbf{Ryan Larson}. ``Overrating Bruins, Underrating Lobos: Media, Prestige, and College Basketball." Presented at The Sixth International Conference on Sport and Society, Toronto, Canada.

\item[\textbf{2014}] \textbf{Larson, Ryan}. ``Fear and Loathing in Minnesota: A Multilevel Analysis of Factors Influencing Crime Fears." Presented at the Midwestern Sociological Society Annual Meeting, Omaha, NE.

\item Lindner, Andrew, \textbf{Ryan Larson}, and John Stelter. ``The Rise and Fall of Citizen Journalism." Presented at the Midwestern Sociological Society Annual Meeting, Omaha, NE. 

\item \textbf{Larson, Ryan}. ``Fear and Loathing in Minnesota: A Multilevel Analysis of Factors Influencing Crime Fears." Presented at the Concordia College Celebration of Student Scholarship: Spotlight Session. Moorhead, MN. 


\end{publist}


\section*{\textbf{Teaching and Mentorship}}

\subsection*{Courses Designed and Taught}


\begin{publist} 

\item Communities and Crime (CJFS 3735), Hamline University
\item Summer Collaborative Undergraduate Research Seminar (INDP 4015), Hamline University
\item Punishment, Corrections, and Society (CJFS 3770), Hamline University
\item Basic Quantitative Methods and Statistics in Criminology (CJFS 1980), Hamline University
\item Research Methods and Data Analysis (CJFS 3140), Hamline University
\item Theories of Criminal Behavior (CJFS 3750), Hamline University
\item Basic Social Statistics (SOC 3811), University of Minnesota
\item Sociology of Neighborhoods (SOC 3081), University of Minnesota

\end{publist}


\subsection*{Mentorship}

\begin{publist}

\item[\textbf{2025}] Hamline University SCUR Program Faculty Mentor: Iris Fuglie
\item[\textbf{2023-2024}] Hamline University Honors Program Faculty Mentor: Molly Hauf
\item[\textbf{2023}] Independent Study - Quantitative Social Science: Madeline Tengel 
\item Hamline University SCUR Program Faculty Mentor: Molly Hauf
\item[\textbf{2020-2021}] Statistics Mentor, UMN Sociology Department
\item[\textbf{2013-2014}] Tutor, Research Methods and Statistics, Professor Nick Ellig, Concordia College

\end{publist}

\section*{\textbf{Media}}

\subsection*{Media Interviews}
\begin{publist} 

\item[\textbf{2024}] Minnesota Public Ratio: Morning Edition. \href{https://www.mprnews.org/story/2024/09/19/black-minneapolis-residents-bear-heaviest-mental-health-burden-after-george-floyds-murder}{``Black Minneapolis residents bear heaviest mental health burden after George Floyd’s murder, new research finds"}. Cathy Wurzer and Gracie Stockton.  

\item The Tennesseean. \href{https://www.tennessean.com/story/news/2024/10/10/tn-has-highest-felony-disenfranchisement-rate-in-nation-report-finds/75597410007/}{``One in 13 Tennessee adults can't vote this election, the most in the country, report finds"}. Evan Mealins. 

\item Red Pers. \href{https://redpers.nl/}{``The right to vote in the United States"}. Bram Kleijne.

\item[\textbf{2023}] Star Tribune. \href{https://www.startribune.com/after-three-most-violent-years-minneapolis-saw-drop-in-crime-summer-but-were-not-back-to-normal-yet/600301635/}{``After three violent years, crime is dropping in Minneapolis"}. Andy Mannix and Jeff Hargarten.  

\end{publist}

\section*{\textbf{Service}}

\subsection*{Department}
\begin{publist}

\item[\textbf{2023}] Search Committee Member for Criminology and Criminal Justice AP
\item[\textbf{2022}] Search Committee Member for Criminology and Criminal Justice AP
\item[\textbf{2017}] UMN Graduate Mentorship Program Co-Coordinator

\end{publist}

\subsection*{University}
\begin{publist}

\item[\textbf{2025}] Pit Orchestra Reed Musician - Urinetown
\item[\textbf{2024}] Hamline Honors Program Faculty Council Member
\item[\textbf{2023-}] Co-Director - Summer Collaborative Undergraduate Research Program (SCUR)
\item[\textbf{2023}] Hamline SCUR Program Selection Committee
\item Social Justice and Social Change Department AP Search Meetings
\item National Conference of Undergraduate Research (NCUR) Chaperone
\item[\textbf{2022-2024}]University and Strategic Planning Committee (USPC) H@mline Data Sub-Committee
\item[\textbf{2022}] Hamline University Campus Climate Survey (DISC) Data Analysis Consultation
\item NCUR Conference Project Selection Committee

\end{publist}

\subsection*{Community}

\begin{publist}

\item[\textbf{2025}] Expert witness and statistician for defense case with the \textit{Legal Rights Center}.

\item Co-author on Policy Brief for Minnesota Pre-Trial Coalition entitled ``Pretrial Data Best Practices \& Linking Databases: The Role of a Unique Identifier" with Dr. Katie Remington, MNJRC.

\item Quantitative Analyst and consultant on \textit{Towards Safety, Liberty, and Equity: A Community-Centered Framework for Redesigning Minnesota's Pretrial System}, a report to the Minnesota legislature by the \textit{Minnesota Justice Research Center}. 

 
\item[\textbf{2024}] Quantitative analyses cited in \textit{The Violence Reduction Project's} January 2025 Report to the Minnesota Legislature.  
\item Quantitative Analyst and Consultant on \textit{Pretrial Best Practices Preliminary Report: Building a Transparent Pretrial Data System}, a report to the Minnesota legislature by the \textit{Minnesota Justice Research Center}.
\item[\textbf{2024-present}] Statistician, \href{https://www.theviolenceproject.org/}{The Violence Project}
\item[\textbf{2023}] Retore the Vote MN Data Visualizations for HF28 Legislative Report
\item[\textbf{2022-present}] Research Consultant, \href{https://www.mnjrc.org/about-us}{Minnesota Justice Research Center}

\begin{itemize}

\item 2022-2023: Driver's License Withdrawals in Minnesota
\item 2023-: Pretrail Best Practices Quantitative Data Lead

\end{itemize}

\item[\textbf{2020}] Minnesota Felon Disenfranchisement Expert Report by Chris Uggen 

\item[\textbf{2013}] Statistical Intern, \href{https://dps.mn.gov/divisions/ojp/statistical-analysis-center/Pages/default.aspx}{Minnesota Department of Public Safety: Office of Justice Programs}, St. Paul, Minnesota
\begin{itemize}
	\item Survey design, data collection, and quantitative analyses published in Hurley Swayze, Dana, and  Buskovick, Dannette. 2014. \href{https://dps.mn.gov/divisions/ojp/forms-documents/Documents/SRO20REPORT.pdf}{``Law Enforcement in Minnesota schools: A Statewide Survey of School Resource Officers."} Minnesota Department of Public Safety: Office of Justice Programs.
\end{itemize}

\end{publist}

\subsection*{Professional Service}

\begin{publist}

\item[\textbf{2024}] Midwest Sociological Society Annual Meeting Session Presider - ``Politics, Power, and Gendered Violence"

\item[\textbf{2023}] Midwest Sociological Society Annual Meeting Session Presider - ``Policing Practices and Responses"

\item[\textbf{2019}] ASA Crime, Law, and Deviance Section Social Media Student Spotlight, December

\item[\textbf{2014-2019}]  Graduate Editorial Board, \href{http://thesocietypages.org/}{\textit{The Society Pages}}
\begin{itemize}
\item Crime and Inequality Topic Page Curator
\item Graphics and Data Visualization Production
\item A catalogue of contributions can be found at \href{https://thesocietypages.org/people/ryanlarson/}{https://thesocietypages.org/people/ryanlarson/}.
\end{itemize}

\end{publist}


\section*{\textbf{Professional Memberships}}
\begin{publist}

\item American Sociological Association
\begin{itemize}
\item - Crime, Law, and Deviance Section
\item - Methodology Section
\item - Communication, Information Technologies, and Media Sociology Section
\end{itemize}
\item American Society of Criminology
\item Midwest Sociological Society

\end{publist}

\section*{\textbf{Reviewer}}

\textit{American Sociological Review, Social Forces, Social Science Research, The Lancet, Socius, Journal of Criminal Justice, Criminal Justice Policy Review, American Journal of Preventative Medicine, Journal of Sport \& Social Issues, and The International Journal of Sport and Society}

\end{document}

